Dissertation Proposal

### 2023-11-07 proposal.tex
sec 7

\subsection{Reduce Syntactic Bias}

@@

@@

  % fill gaps in goal sentences
  \item In the process of developing the goal sentences, we felt the
        existing programs were insufficient to cover the ideas we wanted
        students to work through. For instance, SMoL Quizzes did not
        alias vectors using \lstinline|defvar|, so we added this program:

  \item To reduce the number of concepts, we removed programs that relied
        upon \emph{im}mutable vectors and lists, because they did not
        seem to create problems. (For brevity, we leave these out of
        the presentation of SMoL in \Cref{s:smol}, though they are in the implementation.)

  \item I removed questions related to function equality, which was
        not a focus of the Tutor.\footnote{However, we believe there is
          a good deal of confusion about notions of equality. We
          intend to
          add that as a major tutorial component in future versions.}

  \item I removed programs of a ``Lispy'' nature, such as one where
        the answer depended on whether the reader correctly understood
        this inequality:

        \begin{lstlisting}
      (filter (lambda (n) (> 3 n)) '(1 2 3 4 5))
\end{lstlisting}

        This checks whether $\verb|n| < \verb|3|$, but some presumably
        vocalized it as ``greater than \lstinline|3|, \lstinline|n|?''.

\end{enumerate}
Most of these steps either modify or elide programs. Two cases,
filling gaps in light of the goal sentences and resolving ambiguities,
introduce
programs. Starting with the 37 programs in the SMoL Quizzes, we added
52 more programs to arrive at a total of 89.

In addition to generating this set of programs, we also
modified the answer options. In addition to retaining the correct and
incorrect answers from the SMoL Quizzes (and constructing our best
guess of analogous incorrect answers for the new problems), we added
more wrong answers.

The reason is as follows. The SMoL Quizzes often have very few wrong
choices: of the 37 tasks, 26 have only three choices (including the
correct answer and the ``Other'' option\footnote{In a few cases, we
  removed the \emph{correct} answer from the choices. A student would
  therefore have to click on ``Other'' and type it in. The idea was to
  make the ``Other'' option more salient and plausible.}),
seven have 4, and only four have 5 or 6.
Thus, in most
cases, students have a 25\% or even 33\% chance of just guessing the
right answer or successfully using a process of elimination. By
increasing the number of options, we hoped to
greatly reduce the odds of getting the right answer by chance or
by elimination.

It was important to add wrong answers that are not utterly
implausible, because those would become easy to eliminate. Therefore,
we added numeric constants mentioned in the problem, permuted some of
the values in case of multiple outputs, and so on. In general, we
ended up increasing the number of choices substantially:
only 8 out of the 89 questions have three or four choices; 70
questions have 5--8 choices; and 11 questions have 9--14 choices. I hope
this reduced both guessing and elimination, and forced students to
actually think through the program. Of course, these new answers do
not have a clear associated misconception, so their mistakes are given
the generic explanation.

>>>>

\subsection{Reduce Syntactic Bias}%
\label{s:reduce-syntactic-bias}

@@

  % fill gaps in goal sentences
  \item I felt the existing programs were insufficient to cover the
        ideas we wanted students to work through. For instance, SMoL
        Quizzes did not alias vectors using \lstinline|defvar|, so we
        added this program:

  \item To reduce the number of concepts, I removed programs that
        relied upon \emph{im}mutable vectors and lists, because they
        did not seem to create problems. (For brevity, I leave these
        out of the presentation of SMoL in \Cref{s:smol}, though they
        are in the implementation.)

  \item I removed questions related to function equality, which was
        not a focus of the Tutor.

  \item I removed programs of a ``Lispy'' nature (See
        \Cref{s:reduce-syntactic-bias}).

\end{enumerate}
Most of these steps either modify or elide programs. Two cases,
filling gaps in light of the goal sentences and resolving ambiguities,
introduce programs. Starting with the 37 programs in the SMoL Quizzes,
I added 52 more programs to arrive at a total of 89.

In addition to generating this set of programs, I also modified the
answer options. In addition to retaining the correct and incorrect
answers from the SMoL Quizzes (and constructing our best guess of
analogous incorrect answers for the new problems), I added more wrong
answers to for the reasons given in \Cref{s:interpreting-tasks}. In
general, I ended up increasing the number of choices substantially:
only 8 out of the 89 questions have three or four choices; 70
questions have 5--8 choices; and 11 questions have 9--14 choices.

@@
